```{r echo=FALSE,warning=FALSE,message=FALSE}
source(paste0(getwd(),"/sovi_maps.R"))
```

Baseline SoVI Map
===

```{r SoVI_all,echo=FALSE, fig.height=10,fig.width=15,warning=FALSE,message=FALSE,dev='png'}

reg<-prep4DropOne(path,reg.type,reg.name)

#Plot SoVI scores - assign to reg.name for output
mapSoVI(reg,outName)

```

Drop One Results
===

Drop-One Maps
---

```{r SoVI_drop,echo=FALSE, fig.height=10,fig.width=15,warning=FALSE,message=FALSE,dev='png',eval=FALSE}

#Plot drop-one maps
mapDropOne(path,reg.type,inData=reg,outName)

```

Maps of Change between baseline SoVI and simulation SoVI
---

These maps compare baseline SoVI to SoVI calculated when a given variable is dropped.

*(To condense breaks to tertiles, set "condense.breaks" in the source code to TRUE)*

```{r SoVI_chg_drop,echo=FALSE, fig.height=10,fig.width=15,warning=FALSE,message=FALSE,dev='png'}

for (var in SoVI_vars){

  mapCompareVar(path,reg.name,reg.type,sovi_var=var,by.type="drop",map.quantile=TRUE,condense.breaks=FALSE,return.map_df=TRUE)

}  
```

Margin-of-Error Simulation Results
===

Histogram
---

```{r SoVI_sim_histogram,echo=FALSE, fig.height=15,fig.width=20,warning=FALSE,message=FALSE,dev='png'}

#Reload region for sim results 
#Keep cont_US false for plotting histograms 
reg<-getRegionByQuery(path,reg.name,reg.type)

#Prep reg for simulation results 
reg<-simStats(inData=reg,path,reg.type,reg.name)

#Plot histograms
plotSimHistogram(path,inData=reg,outName,opr="rowMeans")

```


Maximum - Minimum Change in Rank Maps
---

```{r SoVI_sim_MaxMin,echo=FALSE, fig.height=10,fig.width=15,warning=FALSE,message=FALSE,dev='png'}

#Max-min range rank change maps 
mapMaxMin(path,reg,outName)

```


Maps of Change between baseline SoVI and simulation SoVI
---

These maps compare baseline SoVI to SoVI calculated for the MOE simulation of a given variable with the most observed movement in rank from baseline SoVI.

*(To condense breaks to tertiles, set "condense.breaks" in the source code to TRUE)*

```{r SoVI_chg_sim,echo=FALSE, fig.height=10,fig.width=15,warning=FALSE,message=FALSE,dev='png',eval=FALSE}

for (var in SoVI_vars){

  mapCompareVar(path,reg.name,reg.type,sovi_var=var,by.type="sim",map.quantile=TRUE,condense.breaks=FALSE,return.map_df=TRUE)

}  
```
